---
title: 'Welcome to the prodigalverse'
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(prodigalverse)
```

## What is the prodigalverse?

An ever expanding opinionated package of R functions with the same underlying philosophy of doing one thing at a time and one thing only %>% obviating burdensome overhead and steep learning curve of understanding overall generalisations of operations %>% turning one into a prodigy of data analysis %>% this should be of great benefit to new practicioners of data mining and machine learning applications %>% data wranglers and other kinds of analyst should also find use in this library %>% we are aiming at an audience of analysts who are looking for practical results and who are less concerned with the grand concepts which are primarily of interest to researchers but not necessarily for real world practioners

## Writing and working the prodigal way

All help and instructions for the prodigalverse utilise the magrittr "%>%" to highlight the connectivity of
concepts passing one easily into the other to clarify the steps and increase readability of the documentation 
rather than relying on potentially confusing embedded punctuation concepts of the older language such as ".", 
";", "--" %>% we have however retained the comma because of its functional similarity to "%>%" but which is also  different %>% this pays hommage to previously used language functional structures in cases where these older punctuation structures retain their merit under the efficient new paradigm of the prodigalverse %>% we have mixed opinions about uppercase letters

## A grammar of prodigy

we recommend thinking of your analyses in the prodigalverse as 'prodigious' and grammar should follow accordingly %>%

verb = prodigise

adverb = prodigiously

noun = prodigy

adjective = prodigal

## Installing other packages

We strongly recommend that when using the prodigalverse that users install and load every library on CRAN %>%
although functions from these libraries will not always be used and they are not dependencies of the prodigalverse, we believe that it useful to have that functionality available for analyses should the need arise without having to install and load a package in the middle of an analysis

# Phase 1: the C-series of functions
This incredibly useful series of functions were the first additions to the prodigalverse and allow one to
careful build a vector of data in steps %>% this close connection to the data means that the analyst becomes
deeply familiar with their data having actively inspected and inputed all the values %>% this has been implemented at present for vectors up to length 10 only but we are currently looking for collaborators to create functions to populate vectors up to length 10^6, matrices of dimension 10^6 x 10^6 and to arrays of up to 10^6 dimensions %>% although it is conceivable that there are cases where one would need larger data structures, we consider these special cases and we would refer those analysts to base R functions for such peculiar situations

```{r c.series}
x <-5
x<- c2(x, position2x=8) 
x<- c3(x, position3x=17.86) 
x
```

It is clear to see from these examples how one can build a vector of values %>% the true power of the C-series 
of functions becomes apparent if we string the functions together with the magrittr to build up the vector %>% which we will now call the pgvector


```{r c.series.power}
require(magrittr)

x <- 12
full.vector<-
 x %>%
  
 c2(.,position2x=5) %>%
  
  c3(.,position3x=18) %>%
  
    c4(.,position4x=4.1) %>%
  
     c5(.,position5x=126.3) %>%
  
      c6(.,position6x=78) %>%
  
        c7(.,position7x=0.1) %>%
  
          c8(.,position8x=2) %>%
  
            c9(.,position9x=53) %>%
  
              c10(.,position10x=51) %>%
 print
```

## Future plans
We are also currently developing a series of functions that can multiply each element of a vector, matrix or array by a value %>% this series of functions may take some time to get up and running because in order to keep it understandable and simple, we must develop a separate series of functions for each kind of operation such as
addition, subtraction, multiplication, division, square root, cube root, fourth root, square, cube, factorial 
etc %>% when developed, we anticipate that the simplicity of this set of functions will be a gateway into modern results based analysts who are not making production level code but who need to achieve specific
aims

# Looking for collaborators
We welcome contributors sharing our philosophy %>% aside from the areas mentioned above, we are seeking collaborators who could work on developing functions for a beautiful plotting series of functions, deconstructing data structures element by element and of course any other kind of analysis the community might find useful

## Contracting
We are willing to provide contract based help and analysis %>% please email us with a description of 
your help or analysis issue, preferably a sample data set and we can provide you with a detailed evaluation 
of what would be involved and a quote

prodigalverse@protonmail%>%com

You are welcome and we wish you prodigious code and analysis!
